%-------------------------
% Resume in Latex
% Author : Shubhi Rani
% License : MIT
%------------------------
\documentclass[letterpaper,10.8pt]{article}
\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[pdftex]{hyperref}
\usepackage{fancyhdr}
\usepackage{fontawesome}
\usepackage{array} % for m column type
\usepackage{tabularx} % for tabularx environment
\usepackage{soul}

\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.375in}
\addtolength{\evensidemargin}{-0.375in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.5in}
\addtolength{\textheight}{1in}

\urlstyle{rm}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{-3pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

%-------------------------
% Custom commands
\newcommand{\resumeItem}[2]{
  \item\small{
    \textbf{#1}{: #2 \vspace{-2pt}}
  }
}

\newcommand{\resumeItemWithoutTitle}[1]{
  \item\small{
    {\vspace{-2pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-1pt}\item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-5pt}
}


\newcommand{\resumeSubItem}[2]{\resumeItem{#1}{#2}\vspace{-4pt}}
\renewcommand{\labelitemii}{$\circ$}
\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=*]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

%-------------------------------------------
%%%%%%  CV STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{document}
%----------HEADING-----------------
% Create a tabular table with three columns
\begin{tabularx}{\textwidth}{>{\raggedright\arraybackslash}m{0.33\textwidth}>{\centering\arraybackslash}m{0.33\textwidth}>{\raggedleft\arraybackslash}m{0.33\textwidth}}
    % First row
    % Left column: Address
    209 North River St. & 
    % Center column: empty
    & 
    % Right column: Email
    (845) 522-2002 \\
    % Second row
    % Left column: City and state
    Athens, PA 18810 & 
    % Center column: Name
    \textbf{{\LARGE Bradley M. Cardona}} & 
    % Right column: Personal website
    \href[pdfnewwindow=true]{mailto:bcardona300@gmail.com}{bcardona300@gmail.com} \\
    % Third row
    % Left column: Github link
    \href[pdfnewwindow=true]{https://github.com/bmcardona}{www.github.com/bmcardona} & 
    % Center column: empty
    & 
    % Right column: Mobile
    \href[pdfnewwindow=true]{https://www.bcardona.com}{www.bcardona.com} \\
\end{tabularx}

%-----------EDUCATION-----------------
\section{Education}
\resumeSubHeadingListStart
\resumeSubheading
{Allegheny College}{Meadville, PA}
{B.S. Mathematics (GPA: 3.55)}{Aug 2019 - May 2023}
\resumeItemListStart
\resumeItem{Honors}
{Cum Laude}
\resumeItem{Selected Coursework}
{Linear Algebra, Introduction to Real Analysis, Vector Calculus and Variables, Probability/Statistic Inferences I, Probability/Statistic Inferences II, Optimization and Approximation, Complex Variables}
\resumeItemListEnd
\resumeSubHeadingListEnd

%-------- CERTIFICATES ------------
\section{Certificates}
\resumeSubHeadingListStart
\resumeSubItem{\href[pdfnewwindow=true]{https://www.coursera.org/account/accomplishments/specialization/certificate/X54K9A8GBQQF}{\underline{\smash{Google Data Analytics Professional Certificate}}} (2023)}
{Developed an advanced understanding and proficiency of platforms for effective data analyses, including spreadsheets, SQL, R, and Tableau.}
\resumeSubItem{\href[pdfnewwindow=true]{https://www.coursera.org/account/accomplishments/specialization/certificate/T9DME8DMA9L5}{\underline{\smash{Machine Learning Specialization}}} (2023)}
{Studied supervised learning (linear regression, logistic
regression, neural networks, decision trees), unsupervised learning
(clustering, anomaly detection), recommender systems, and
reinforcement learning; learned some of the best practices for machine learning models; and gained practical skills to apply machine learning techniques.}
\resumeSubHeadingListEnd

%-----------INTERNSHIPS-----------------
\section{Internships}
  \resumeSubHeadingListStart
    \resumeSubheading
    {Allegheny College Mathematics Department}{Meadville, PA}
    { Undergraduate Researcher }{May 2022 -  Jul 2022}
    \begin{itemize}
        \item{Studied mathematics under the supervision of Professor Caryn Werner.}
        \item{Explored systems of algebraic curves in the projective plane, a topic in algebraic geometry.}
        \item{Solved equations and visualized graphs using Wolfram Mathematica and the Wolfram Language.}
        \item{Presented my work to students and faculty of Allegheny College, as part of the ACRoSS seminar series.}
    \end{itemize}
\resumeSubHeadingListEnd

%-----------PROJECTS-----------------
\section{Software Projects}
\resumeSubHeadingListStart
\resumeSubItem{Personal website}{\href[pdfnewwindow=true]{https://www.bcardona.com}{\href[pdfnewwindow=true]{www.bcardona.com}{\underline{\smash{www.bcardona.com}}}} (for additional information and projects)}

\resumeSubItem{Overpopulation Case Study (\textnormal{\href[pdfnewwindow=true]{https://github.com/BMCARDONA/fertility_rates_case_study/blob/main/fertility_rates.pdf}{\underline{\smash{Paper}}}}, \textnormal{\href[pdfnewwindow=true]{https://public.tableau.com/app/profile/bradley.cardona/viz/AverageFertilityRatebyRegion1960-2021/Dashboard2}{\underline{\smash{Tableau}}}}, \textnormal{\href[pdfnewwindow=true]{https://github.com/BMCARDONA/fertility_rates_case_study/tree/main}{\underline{\smash{GitHub}}}})}{} 



% \href[pdfnewwindow=true]{https://www.bcardona.com}{\href[pdfnewwindow=true]{link}{\underline{\smash{project}}}} 

  \begin{itemize}
    \item Conducted a study to explore the trends of average total fertility rates across large geographical regions from 1960 to 2021.
    \item Concluded that most countries will need to address an underpopulation problem.
    \item \underline{Utilized}: R, Tableau, Excel, Git, GitHub
  \end{itemize}
\resumeSubItem{Deep Work Tracker \href[pdfnewwindow=true]{https://github.com/bmcardona/deep_work_tracker}{(\textnormal{\underline{\smash{GitHub}})}}}{}
  \begin{itemize}
    \item{Developed a Python project to track and record focused work activities, known as ``deep work'', to improve my productivity.}
    \item{Implemented a CSV file-based system for logging daily accomplishments and a Python script for generating visualizations and a daily/monthly summary.}
    \item{\underline{Utilized}: Python, Pandas, Matplotlib, Seaborn, Git, GitHub}
  \end{itemize}
\resumeSubItem{Pathfinding Visualizer \href[pdfnewwindow=true]{https://bcardona.com/pathfinding-visualizer/}{(\textnormal{\underline{\smash{Website}}}, \href[pdfnewwindow=true]{https://github.com/BMCARDONA/pathfinding-visualizer}{\textnormal{\underline{\smash{GitHub}}})}}}{}
    \begin{itemize}
        \item{Developed an immersive JavaScript web application to visualize various search algorithms. }
        \item{Implemented Depth-First Search, Breadth-First Search, A* Search, Greedy Best-First Search, and Dijkstra’s algorithm. }
        \item{\underline{Utilized}: JavaScript, HTML, CSS, Git, GitHub}
    \end{itemize}
    \resumeSubItem{Sorting Visualizer \href[pdfnewwindow=true]{https://bcardona.com/sorting-visualizer/}{(\textnormal{\underline{\smash{Website}}}, \href[pdfnewwindow=true]{https://github.com/BMCARDONA/sorting-visualizer}{\textnormal{\underline{\smash{GitHub}}})}}}{}
    \begin{itemize}
        \item{Built an interactive JavaScript web application to visualize a range of sorting algorithms.}
        \item{Implemented Bubble Sort, Heap Sort, Insertion Sort, Quick Sort, and Selection Sort.}
        \item{\underline{Utilized}: JavaScript, HTML, CSS, Git, GitHub}
    \end{itemize}
% \resumeSubItem{Sudoku \href[pdfnewwindow=true]{https://bcardona.com/sudoku-solver/}{\faExternalLink}}{}
%     \begin{itemize}
%         \item{Built VanillaJS application for playing Sudoku.}
%         \item{Implemented four board difficulties: easy, medium, hard, and impossible.}
%         \item{\underline{Utilized}: JavaScript, HTML, CSS, Git, GitHub}
%     \end{itemize}
% \resumeSubItem{Portfolio Template \href[pdfnewwindow=true]{https://bcardona.com/personal-website-js/}{\faExternalLink}}{}
%     \begin{itemize}
%         \item{Built template using React to showcase recently updated GitHub projects.}
%         \item{Used Github’s REST API to show automatically when update has been made to GitHub repository.}
%         \item{\underline{Utilized}: ReactJS, Git, GitHub}
%     \end{itemize}
  \resumeSubHeadingListEnd

%--------TECHNICAL SKILLS------------
\section{Skills}
\resumeSubHeadingListStart
\resumeSubItem{Languages}{Python, R, SQL, JavaScript, LaTeX, HTML, CSS}
\resumeSubItem{Libraries/Frameworks}{TensorFlow, NumPy, Matplotlib, Microsoft Excel, GitHub, Git}
\resumeSubHeadingListEnd

%--------SOFT SKILLS------------
% \section{Soft Skills}
% \resumeSubHeadingListStart
% \resumeSubItem{Strong}{Communication, Collaboration, Attention to detail, Perseverance, Adaptability}
% \resumeSubHeadingListEnd
% %-------------------------------------------
\end{document}